Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-08 main_paper.tex
Fix a typo in Algorithm 1
Kernel weights on the RHS (LHS) was used to estimate coefficients on the
LHS (RHS).

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, define the scaled kernel functions
\begin{align*}
  K_h(x) &= \tfrac{1}{h} K(x/h)
\intertext{and}
  K_b(x) &= \tfrac{1}{b} K(x/b).
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice.  Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.  For simplicity, though, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_{-} &= \{i : X_i < 0 \}, &
    I_{+} &= \{i : X_i > 0 \}.
  \end{align*}
  Also define $M_{-}$ and $M_{+}$ to be the number of elements in $I_{-}$ and
  $I_{+}$ respectively, and $m_{-}(1),\dots,m_{-}(M_{-})$ and
  $m_{+}(1),\dots,m_{+}(M_+)$ to be subsequences of $1,\dots,n$ that index
  $I_-$ and $I_+$, respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
    the observations in $I_-$ and $I_+$ and the kernel $K_{b}(X_{i})$:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
    \end{align*}
    Let
    \[
      \hat g(x) = \begin{cases}
        \hat g_-(x) & \textif\ x < 0 \\
        \hat g_+(x) & \otherwise
      \end{cases}
    \]
    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$.
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}).
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

@@

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
comparable with theirs and with the rest of the literature. They use this experimental design with a constant $\sigma_i = 0.1295$. We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity. When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT. When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined. For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
    \midrule                                                     \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
\end{align*}
and
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}(h)
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}(h)
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

Also, for reference, define the variance terms
\begin{equation*}
  V(h)
  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
\end{equation*}
and
\begin{multline*}
  C(h,b) =
  n^{-1} e_2' \Big[
    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
    \Big] e_2 \\
  - 2 h^2 n^{-1} b^{-2}
    e_0' \Big[
    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
    \Big] e_2.
\end{multline*}
See CCT for the motivation and derivation of these formulas.

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{align*}
  \hat\beta^*_{+,p} - \beta^*_{+,p}
  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
  \hat\beta^*_{-,p} - \beta^*_{-,p}
  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
\end{align*}
ensuring that
\begin{align*}
  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely. Consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

>>>>

\begin{assumption}[Bandwidth and kernel]\label{A2}
  Let $h$ be the bandwidth used to estimate the local linear model and let
  $b$ be the bandwidth used to estimate a second local quadratic model. Then
  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
    Unless otherwise stated, all limits in this paper are assumed to hold as
    $n \to \infty$.}
  The kernel function $K$ is positive and continuous on the interval
  $[-\kappa,~\kappa]$ and zero outside that interval.
\end{assumption}
To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
define the scaled and truncated kernel functions
\begin{align*}
  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
\intertext{and}
  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
\end{align*}
Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
in practice. Note that different kernel functions could be used for the
treatment effect estimator and the higher order approximation used for the
bootstrap.\footnote{%
  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
  would not affect our proofs.} %
For simplicity, however, we use the same function for all steps of
estimation in this paper.  Potentially different kernel functions and bandwidths
could also be used for estimation below and above the cutoff, but we again focus
on the simpler case here.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2}.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$
    with least squares using $K_{-,b}$ and $K_{+,b}$ for weights:
    \begin{align}
      \label{eq:2}
      \hat g_{-}(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
      &\hat g_{+}(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
    \end{align}
    with
    \begin{align*}
      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
    \end{align*}
    Let
    \[
      \hat g(x) = \begin{cases}
        \hat g_-(x) & \textif\ x < 0 \\
        \hat g_+(x) & \otherwise
      \end{cases}
    \]
    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$ for all $i$.
  \item Repeat the following steps $B_{1}$ times to produce the
    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
    $k$th replication:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
      \end{align*}
      for all $i$.
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$ for
      weights:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i =1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{-,h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_i^* - \mu - \beta X_i)^2 K_{+,h}(X_{i}).
      \end{align*}
    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:9}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation}
  \end{enumerate}
\end{algorithm}
Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
distribution induced by this bootstrap. The bootstrap estimator works by
constructing an approximate DGP with known properties. As the dataset gets
larger, the approximate DGP mimics the unknown real DGP more closely, and the
population parameter values in the bootstrap DGP can become accurate estimates
of the true parameter values in the real DGP.

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{equation*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \end{equation*}
  and
  \begin{multline*}
    \sup_{x,\tau}
    \Big\rvert \Pr^*\big[ \sqrt{nh}
    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
    - \Pr\big[ \sqrt{nh}
    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
  \end{multline*}
\end{theorem}

@@

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2),
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature. We
will use the same three functional forms for $\mu_{j}$ as CCT as well.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
    \midrule
    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
        & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
        & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

@@

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Much of the theory in this appendix applies to both
sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
implies that
\begin{align*}
  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
\end{align*}
with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
These coefficients are related to the quantities of interest by
\begin{equation*}
  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
\end{equation*}
for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
\begin{equation*}
  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
\end{equation*}

For reference, define the variance terms
\begin{equation*}
  V(h)
  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
    \Gamma_{-,1}(h)^{-1}
  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
\end{equation*}
and
\begin{multline*}
  C(h,b) =
  \tfrac{1}{n} \, e_2' \big[
    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
  \big] e_2 \\
  - \tfrac{2 h^2}{n b^{2}}
    e_0' \Big[
    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
    \Big] e_2.
\end{multline*}
See CCT for more on the motivation and derivation of these formulas.

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{equation*}
  Y_i^* =
  \begin{cases}
    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
  \end{cases}
\end{equation*}
which, along with the definitions at the beginning of the appendix,
ensures that
\begin{align*}
  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed
